---
title: "linear_models"
author: "Alana Ferris"
date: "2022-11-10"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(p8105.datasets)
library(viridis)

set.seed(1)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Prop tests for HW #5

If you have this many successes and this many trials what is the proportion. Null probability is testing against null hypothesis that...Estimated proportion of successes givne that saw 5 success/10 trials. we are interested in this and the confidence interval. This code is what you can use to make the output a little prettier. 

In this homework, start with one city to better understand what you are trying to do. In this dataframe on baltimore, figure out number of successes/trials for baltimore --> a counting problem--> the number of unresolved homicides and number of total homicides and the prop.test will give you a prop test and condifence interval then use broom tidy to pull those things out. Those two things in prop test function, tidy output, extract what you need and then iterate. can you write a function given city's dataframe design a proptest for each city. 

```{r}
prop.test(5,10) %>% 
  broom::tidy() %>% 
  select(estimate, starts_with())
```
# Model fitting

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

Price = the outcome today

## Fit the first model

If looking at stars = 0 how much does it cost in each borough comparatively 
```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)

fit

summary(fit)

fit %>% 
  broom::tidy() %>% 
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 2)
```
Let's change reference category

```{r}
fit = 
  nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough)
  ) %>% 
  lm(price ~ stars + borough, data = .)
  
fit %>% 
  broom::tidy() %>% 
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 2)

fit %>% 
  broom::glance() 
```
lm expects a formula first and then the data, and if first argument isn't a dataframe need to tell it where to find it 

Now not seeing manhattan in output bc it is now the reference catagroy for all the other comparisons. manhattan rn is the most common category bc we used factor infreq to anaylze it this way --> it says most common is category 1 and category 1 is always the reference category in the regression. 

can pipe into `select` to pull out the statistic thing or whatever you are interested in  

# Diagnostics 

How to put residuals into plots
Residuals in this case are literally what?
generally supposed to be mean 0 and constance variance. here constant variance does not work here.
```{r}
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point()

nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = borough, y = resid)) +
  geom_violin() +
  ylim(-250, 250)
``` 

# Hypothesis testing 

one coefficient (in this example, `stars`)

```{r}
fit %>% 
  broom::tidy()

fit_null = lm(price ~ stars, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough, data = nyc_airbnb)

anova(fit_null, fit_alt) %>% 
  broom::tidy()
```

# Room type by borough

interactions...?

```{r}
fit =
  nyc_airbnb %>% 
  lm(price ~ stars + borough * room_type, data = .) 

fit %>%   
  broom::tidy()
```
So...can we fit models by borough...?

df column has the tibbles, lm function needs you to call the data as well 

```{r}
nyc_airbnb %>% 
  nest(df = -borough) %>% 
  mutate(
    models = map(.x = df, ~lm(price ~ stars + room_type, data = .x)), 
    results = map(models, broom::tidy)) %>% 
  select(borough, results) %>% 
  unnest(results)
```
Did the above because its a shorter way to get the same result.. of what lol 
```{r}
nyc_airbnb %>% 
  filter(borough == "Queens") %>% 
  lm(price ~ stars + room_type, data = .) %>% 
  broom::tidy()
```


